04_validation

### 2022-07-25 replication_data/rmd/04_validation.Rmd
Fix v1.1 file bug
arxiv draft

@@

ICBe_events_agreed_markdown <- ICBe_events_agreed %>% left_join(icb_events_long_narratives_sentences)

>>>>

file.copy(flag_folder_small, "/mnt/8tb_a/rwd_github_private/icbewebsite/", recursive=TRUE)

@@

ICBe_events_agreed_markdown <- icb_events_long_narratives_sentences #ICBe_events_agreed %>% left_join(icb_events_long_narratives_sentences %>% dplyr::select(-sentence_span_text) )
